---
output:
  html_document: default
  pdf_document: default
---
```{R}
library(tidyverse)
Streaming1<- read_csv("Streaming1.csv")
Streaming2<- read_csv("Streaming2.csv")
Streaming3<- read_csv("Streaming3.csv")
Streaming4<- read_csv("Streaming4.csv")
NetflixViewingHistory <- read_csv("NetflixViewingHistory.csv")
Streaming<- Streaming1 %>% full_join(Streaming2)
Streaming<- Streaming%>% full_join(Streaming3)
Streaming<- Streaming%>% full_join(Streaming4)
head(Streaming)
head(NetflixViewingHistory)
```


Intro: 
I chose this data because I do a lot of binge watching and I often listen to music, and I thought it would be cool to see how my data would look like all together. 
The netflix data contained the variables date and Title, and the spotify data had the variables endTime(which was time and date), artist name, track name, and ms played. I downloaded my data off of my Netflix and Spotify accounts and then uploaded them to R. 
Often times watching things or listening to music is my little escape (that I get way too carried away with). My first year I was all alone and I had moved to a new city so I did A LOT of binge watching. 
I would expect to see a lot of titles watched in a day for 2017 definitely, and for 2020 I would expect to have more songs listened to than titles watched because I got more into music as a "coping" mechanism, mostly because I did not have the energy to find new shows. 

```{R}
NetflixViewingHistory$Date <- format(as.Date(NetflixViewingHistory$Date, format ="%m/%d/%y"),"%Y-%m-%d")
Streaming <-Streaming %>%separate(endTime, into = c("Date","endTime"), sep = " (?=[^ ]+$)")

TtlStrm <- Streaming %>% full_join(NetflixViewingHistory)
head(TtlStrm)

```

I did a full join because I did not want to lose any data. 
Streaming had 37,485 observations and NetflixViewingHistory had 2,640 observations. No observations were dropped, but some were duplicated. 


```{R}
TtlStrm<- TtlStrm %>% mutate('time(s)' = msPlayed/1000)
TtlStrm<- TtlStrm %>% arrange(Date)
TtlStrm<- TtlStrm%>%separate(Title, into = c("Title","Season"), sep = ":")
head(TtlStrm)

TtlStrm %>% filter(Date == "2020-09-08") 
TtlStrm %>% group_by(artistName) %>% count(sort=T)
TtlStrm %>% group_by(Title) %>% count(sort=T)
TtlStrm %>% group_by(Date) %>% count(sort=T)

```

```{r}

```

My top artist overall was Mac DeMarco, my most watched show was New Girl, and the day with the most activity was June 8, 2020. 

```{r}

```

